### 2018-10-17 tex/abstract.tex
Version 2.2
SongTao revision.

In large-scale data-parallel analytics, shuffle, or the cross-network read and aggregation of partitioned data between tasks with data dependencies, usually brings in large overhead. Due to the dependency constrains, execution of those descendant tasks could be delayed by logy shuffles.
To reduce shuffle overhead, we present \textit{SCache}, an open source plug-in system that particularly focuses on shuffle optimization. 
{\color{blue}
During shuffle optimization process, we propose a performance model called \textit{Framework Resources Quantification}(FRQ) model. 
FRQ model displays utilization of resources in time dimension and calculate execution time of computing jobs on different DAG frameworks. 
We use FRQ model to assist in analyzing shuffle process and verify SCache shuffle optimization by mathematics.
}
By extracting and analyzing shuffle dependencies prior to the actual task execution, SCache can adopt heuristic pre-scheduling combining with shuffle size prediction to pre-fetch shuffle data and balance load on each node. 
Meanwhile, SCache takes full advantage of the system memory to accelerate the shuffle process. 
% {\color{red}
% We have implemented SCache and customized Spark to use it as the external shuffle service and co-scheduler. The performance of SCache is evaluated with both simulations and testbed experiments on a 50-node Amazon EC2 cluster.
% Those evaluations have demonstrated that, by incorporating SCache, the shuffle overhead of Spark can be reduced by nearly $89\%$, and the overall completion time of TPC-DS queries improves $40\%$ on average.
% }
{\color{blue}
We have implemented SCache as the external shuffle service and co-scheduler on both Apache Spark and Apache Hadoop. The performance of SCache is evaluated with both simulations and testbed experiments on a 50-node Amazon EC2 cluster.
Those evaluations have demonstrated that, by incorporating SCache, the shuffle overhead of Spark can be reduced by nearly $89\%$, and the overall completion time of TPC-DS queries improves $40\%$ on average. On Apache Hadoop, SCache optimize end-to-end Terasort completion time by 15\%.
}
\end{abstract}

>>>>

In large-scale data-parallel analytics, shuffle, or the cross-network read and aggregation of partitioned data between tasks with data dependencies, usually brings in large overhead. Due to the dependency constrains, execution of those descendant tasks could be delayed by logy shuffles.
To reduce shuffle overhead, we present \textit{SCache}, an open source plug-in system that particularly focuses on shuffle optimization. 
{\color{blue}
During shuffle optimization process, we propose a performance model called \textit{Framework Resources Quantification} (FRQ) model. 
The FRQ model displays utilization of resources in the time dimension and calculates execution time of computing jobs on different DAG frameworks. 
We use FRQ model to assist in analyzing shuffle process and verify SCache shuffle optimization by mathematics.
}
By extracting and analyzing shuffle dependencies prior to the actual task execution, SCache can adopt heuristic pre-scheduling combining with shuffle size prediction to pre-fetch shuffle data and balance load on each node. 
Meanwhile, SCache takes full advantage of the system memory to accelerate the shuffle process. 
% {\color{red}
% We have implemented SCache and customized Spark to use it as the external shuffle service and co-scheduler. The performance of SCache is evaluated with both simulations and testbed experiments on a 50-node Amazon EC2 cluster.
% Those evaluations have demonstrated that, by incorporating SCache, the shuffle overhead of Spark can be reduced by nearly $89\%$, and the overall completion time of TPC-DS queries improves $40\%$ on average.
% }
{\color{blue}
We have implemented SCache as the external shuffle service and co-scheduler on both Apache Spark and Apache Hadoop. The performance of SCache is evaluated with both simulations and testbed experiments on a 50-node Amazon EC2 cluster.
Those evaluations have demonstrated that, by incorporating SCache, the shuffle overhead of Spark can be reduced by nearly $89\%$, and the overall completion time of TPC-DS queries improves $40\%$ on average. On Apache Hadoop, SCache optimizes end-to-end Terasort completion time by $15\%$.
}
\end{abstract}

### 2018-10-17 tex/evaluation.tex
SongTao revision.

\begin{figure}
	\includegraphics[width=\linewidth]{fig/scache_util}
	\caption{CPU utilization and I/O throughput of a node during a Spark single shuffle application With SCache}
	\label{fig:scache_util}
\end{figure}

In order to prove the performance gain of SCache with a real production workload, we also evaluate Spark TPC-DS\footnote{https://github.com/databricks/spark-sql-perf} and present the overall performance improvement.
{\color{blue}
To prove SCache compatibility as a cross-framework plug-in, we implemented SCache on both Hadoop MapReduce and Spark. 
Due to the simple DAG computing in Hadoop MapReduce, we only use Terasort as a shuffle-heavy benchmark to evaluate the performance of Hadoop MapReduce with SCache.
}
Finally, we measure the overhead of weighted reservoir sampling. 
In summary, SCache can decrease ~$89\%$ time of Spark shuffle without introducing extra network transfer.
More impressively, the overall completion time of TPC-DS can be improved ~$40\%$ on average by applying the optimization from SCache.
{\color{blue}Meanwhile, Hadoop MapReduce with SCache optimize job completion time by up to 15\% and an average of 13\%}

@@

% \begin{figure}
% 	\begin{subfigure}{\linewidth}
% 		\centering
% 		\includegraphics[width=0.6\linewidth]{fig/groupbymaptask}
% 		\caption{Median Task Details in Map Stages}
% 		\label{fig:maptask}
% 	\end{subfigure}
% 	\begin{subfigure}{\linewidth}
% 		\centering
% 		\includegraphics[width=0.6\linewidth]{fig/groupbyreducetask}
% 		\caption{Median Task Details in Reduce Stages}
% 		\label{fig:reducetask}
% 	\end{subfigure}
% 	\caption{Median Task Completion Time of Single Shuffle Test}
% 	\label{fig:singleshuffletask}
% \end{figure}
The performance evaluation in Figure \ref{fig:singleshuffletask} shows the consistent results with our observation of hardware utilization. 
% By running Spark with SCache, the completion time of map stage can be reduced $10\%$ on average. 
% For reduce stage, instead, SCache achieves a ~$75\%$ performance gain in the completion time of the reduce stage.
% A detail analysis into the nutshell of varied overall performance gain on different stages is presented with Figure \ref{fig:singleshuffletask}. 
For each stage, we pick the task that has median completion time. 
In the map task, the disk operations are replaced by the memory copies to decouple the shuffle write. 
It helps eliminate ~40\% of shuffle write time (Figure \ref{fig:maptask}), which leads to a $10\%$ improvement of map stage completion time in Figure \ref{fig:mapstage}. 
Note that the shuffle write time can be observed even with the optimization of SCache. 
The reason is that before moving data out of Spark's JVM, the serialization is inevitable and CPU intensive \cite{makingsense}.

@@

Figure \ref{fig:hadoop_terasort} shows the hardware resource utilization of Hadoop MapReduce running Terasort. Both figures have the same proportion of time. Hadoop MapReduce with SCache brings 15\% of total time optimization with 384GB input data size. 
As shown in Figure \ref{fig:hadoop_terasort_origin}, Hadoop MapReduce without SCache writes intermediate data locally in the map phase. The shuffle phase and reduce phase start simultaneously. Because a large amount of shuffle data reaches the network bottleneck, the beginning part of reduce needs to wait for network transfer. This causes the CPU resources to be idle. 
As shown in Figure \ref{fig:hadoop_terasort_scache}, Hadoop MapReduce with SCache start pre-fetching in the map phase. This avoids the reduce phase waiting for the shuffle data. Furthermore, pre-fetching utilizes the idle IO throughput in the map phase. As shown in Figure \ref{fig:hadoop_terasort_time}, after better fine-grained utilization of hardware resources, Hadoop MapReduce with SCache optimize Terasort overall completion time by up to 15\% and an average of 13\% with input data sizes from 128GB to 512GB.
}

@@

\subsection{Production Workload}
We also evaluate some queries from TPC-DS\footnote{http://www.tpc.org/tpcds/}. 
TPC-DS benchmark is designed for modeling multiple users submitting varied queries (e.g. ad-hoc, interactive OLAP, data mining, etc.). 
TPC-DS contains 99 queries and is considered as the standardized industry benchmark for testing big data systems. 
% We evaluate the performance of Spark with SCache by picking some of the TPC-DS queries with shuffle intensive attribute. 
As shown in Figure \ref{fig:tpcds}, the horizontal axis is query name and the vertical axis is query completion time. 
Note that we skip some queries due to the compatible issues. 
Spark with SCache outperforms the original Spark in almost all tested queries. 
Furthermore, in many queries, Spark with SCache outperforms original Spark by an order of magnitude. 
It is because that those queries contain shuffle-heavy operations such as "groupby", "union", etc.
The overall reduction portion of query time that SCache achieved is 40\% on average. 
Since this evaluation presents the overall job completion time of queries, we believe that our shuffle optimization is promising.
% \begin{figure}
% 	\begin{subfigure}{\linewidth}
% 		\centering
% 		\includegraphics[width=0.6\linewidth]{fig/tera}
% 		\caption{Reduce Stage Completion Time Comparison of First Shuffle}
% 		\label{fig:terasort}
% 	\end{subfigure}
% 	\vspace{0.08cm}
% 	\begin{subfigure}{\linewidth}
% 		\centering
% 		\includegraphics[width=0.6\linewidth]{fig/tera_shuffle}
% 		\caption{Shuffle Data through Network Comparison of Second Shuffle}
% 		\label{fig:terashuffle}
% 	\end{subfigure}
% 	\caption{Terasort Evaluation}
% \end{figure}
\subsection{Overhead of Sampling}
We evaluate the overhead of sampling with different input sizes and numbers of nodes. 
In Figure \ref{fig:sampling}, the overhead of sampling only grows with the increase of input size on each node, but remains relatively stable when the cluster size scales up.
Since the shuffle data is short-lived, write-once, and read-once, the central controller of SCache does not have to collect and manage complex metadata. 
Meanwhile, most of the optimizations such as fetching and storing shuffle data are finished by workers independently. 
So the cost of pre-scheduling algorithm and memory management are unlikely to make the master become the bottleneck of the scalability.
Combined with the sampling overhead evaluation, we believe that SCache is scalable.

>>>>

\begin{figure}
	\includegraphics[width=\linewidth]{fig/scache_util}
	\caption{CPU utilization and I/O throughput of a node during a Spark single shuffle application with SCache}
	\label{fig:scache_util}
\end{figure}

In order to prove the performance gain of SCache with a real production workload, we also evaluate Spark TPC-DS\footnote{https://github.com/databricks/spark-sql-perf} and present the overall performance improvement.
{\color{blue}
To prove the compatibility of SCache as a cross-framework plug-in, we implemented SCache on both Hadoop MapReduce and Spark. 
Due to the simple DAG computing in Hadoop MapReduce, we only use Terasort as a shuffle-heavy benchmark to evaluate the performance of Hadoop MapReduce with SCache.
}
Finally, we measure the overhead of weighted reservoir sampling. 
In summary, SCache can decrease ~$89\%$ time of Spark shuffle without introducing extra network transfer.
More impressively, the overall completion time of TPC-DS can be improved ~$40\%$ on average by applying the optimization from SCache.
{\color{blue}Meanwhile, Hadoop MapReduce with SCache optimizes job completion time by up to $15\%$ and an average of $13\%$}

@@

% \begin{figure}
% 	\begin{subfigure}{\linewidth}
% 		\centering
% 		\includegraphics[width=0.6\linewidth]{fig/groupbymaptask}
% 		\caption{Median Task Details in Map Stages}
% 		\label{fig:maptask}
% 	\end{subfigure}
% 	\begin{subfigure}{\linewidth}
% 		\centering
% 		\includegraphics[width=0.6\linewidth]{fig/groupbyreducetask}
% 		\caption{Median Task Details in Reduce Stages}
% 		\label{fig:reducetask}
% 	\end{subfigure}
% 	\caption{Median Task Completion Time of Single Shuffle Test}
% 	\label{fig:singleshuffletask}
% \end{figure}
The performance evaluation in Figure \ref{fig:singleshuffletask} shows the consistent results with our observation of hardware utilization. 
% By running Spark with SCache, the completion time of map stage can be reduced $10\%$ on average. 
% For reduce stage, instead, SCache achieves a ~$75\%$ performance gain in the completion time of the reduce stage.
% A detail analysis into the nutshell of varied overall performance gain on different stages is presented with Figure \ref{fig:singleshuffletask}. 
For each stage, we pick the task that has median completion time. 
In the map task, the disk operations are replaced by the memory copies to decouple the shuffle write. 
It helps eliminate $40\%$ of shuffle write time (Figure \ref{fig:maptask}), which leads to a $10\%$ improvement of map stage completion time in Figure \ref{fig:mapstage}. 
Note that the shuffle write time can be observed even with the optimization of SCache. 
The reason is that before moving data out of Spark's JVM, the serialization is inevitable and CPU intensive \cite{makingsense}.

@@

Figure \ref{fig:hadoop_terasort} shows the hardware resource utilization of Hadoop MapReduce running Terasort. Both figures have the same proportion of time. Hadoop MapReduce with SCache brings $15\%$ of total time optimization with 384GB input data size. 
As shown in Figure \ref{fig:hadoop_terasort_origin}, Hadoop MapReduce without SCache writes intermediate data locally in the map phase. The shuffle phase and the reduce phase start simultaneously. Because a large amount of shuffle data reaches the network bottleneck, the beginning part of reduce needs to wait for network transfer. This causes CPU resources to be idle. 
As shown in Figure \ref{fig:hadoop_terasort_scache}, Hadoop MapReduce with SCache starts pre-fetching in the map phase. This avoids the reduce phase waiting for the shuffle data. Furthermore, pre-fetching utilizes the idle I/O throughput in the map phase. As shown in Figure \ref{fig:hadoop_terasort_time}, after better fine-grained utilization of hardware resources, Hadoop MapReduce with SCache optimizes Terasort overall completion time by up to $15\%$ and an average of $13\%$ with input data sizes from 128GB to 512GB.
}

@@

\subsection{Production Workload}
We also evaluate some queries from TPC-DS\footnote{http://www.tpc.org/tpcds/}. 
TPC-DS benchmark is designed for modeling multiple users submitting varied queries (e.g. ad-hoc, interactive OLAP, data mining, etc.). 
TPC-DS contains 99 queries and is considered as the standardized industry benchmark for testing big data systems. 
% We evaluate the performance of Spark with SCache by picking some of the TPC-DS queries with shuffle intensive attribute. 
As shown in Figure \ref{fig:tpcds}, the horizontal axis is query name and the vertical axis is query completion time. 
Note that we skip some queries due to the compatible issues. 
Spark with SCache outperforms the original Spark in almost all tested queries. 
Furthermore, in many queries, Spark with SCache outperforms original Spark by an order of magnitude. 
It is because that those queries contain shuffle-heavy operations such as "groupby", "union", etc.
The overall reduction portion of query time that SCache achieved is $40\%$ on average. 
Since this evaluation presents the overall job completion time of queries, we believe that our shuffle optimization is promising.
% \begin{figure}
% 	\begin{subfigure}{\linewidth}
% 		\centering
% 		\includegraphics[width=0.6\linewidth]{fig/tera}
% 		\caption{Reduce Stage Completion Time Comparison of First Shuffle}
% 		\label{fig:terasort}
% 	\end{subfigure}
% 	\vspace{0.08cm}
% 	\begin{subfigure}{\linewidth}
% 		\centering
% 		\includegraphics[width=0.6\linewidth]{fig/tera_shuffle}
% 		\caption{Shuffle Data through Network Comparison of Second Shuffle}
% 		\label{fig:terashuffle}
% 	\end{subfigure}
% 	\caption{Terasort Evaluation}
% \end{figure}
\subsection{Overhead of Sampling}
We evaluate the overhead of sampling with different input sizes and numbers of nodes. 
In Figure \ref{fig:sampling}, the overhead of sampling only grows with the increase of input size on each node, but remains relatively stable when the cluster size scales up.
Since the shuffle data is short-lived, write-once, and read-once, the central controller of SCache does not have to collect and manage complex metadata. 
Meanwhile, most of the optimizations such as fetching and storing shuffle data are finished by workers independently. 
So the cost of pre-scheduling algorithm and memory management are unlikely to make the master become the bottleneck of the scalability.
Combined with the sampling overhead evaluation, we believe that SCache is scalable.

### 2018-10-17 tex/impl.tex
SongTao revision.

\section{Implementation}\label{impl}
This section presents an overview of the implementation of SCache. 
% {\color{red}
% Here we use Spark as an example of DAG framework to illustrate the work flow of shuffle optimization. 
% We will first present the system overview in Subsection \ref{arch} while the following two subsections focus on the two constraints on memory management.
% }
{\color{blue}
We first present the system overview and the detail of sampling in Subsection \ref{arch}. 
The following \ref{memorymanage} subsection focuses on the two constraints on memory management.
In Subsection \ref{crossframework}, we will evaluate cross-framework capability of SCache based on Hadoop MapReduce and Spark. 
At last, we discuss the cost of adapting SCache and fault tolerance. 
}

\subsection{System Overview}\label{arch}
SCache consists of three components: a distributed shuffle data management system, a DAG co-scheduler, and a %{\color{red}daemon inside Spark.}
{\color{blue} worker daemon. As a plug-in system, SCache needs to rely on a DAG framework.} As shown in Figure \ref{fig:architecture}, SCache employs the legacy master-slaves architecture like GFS \cite{gfs} for the shuffle data management system. 
The master node of SCache coordinates the shuffle blocks globally with application context. The worker node reserves memory to store blocks.
The coordination provides two guarantees: (a)data is stored in memory before tasks start and (b)data is scheduled on-off memory with all-or-nothing and context-aware constraints. 
The daemon bridges the communication between %{\color{red}Spark}
{\color{blue} DAG framework} and SCache. The co-scheduler is dedicated to pre-schedule reduce tasks with DAG information and enforce the scheduling results to %{\color{red}Spark scheduler}
 {\color{blue} original scheduler in framework}.

@@

When a map task finishes computing, the shuffle write implementation of DAG framework is modified to call the SCache API and move all the blocks out of {\color{blue}framework worker} through memory copy. 
After that, the slot will be released (without being blocked on disk operations).
When a block of the map output (i.e., "map output" in Figure \ref{fig:shuffle}) is received, the SCache worker will send the block ID and the size to the master.
If the collected map output data reach the observation threshold, the DAG co-scheduler will run the scheduling Algorithm \ref{hminheap} or \ref{mhminheap} to pre-schedule the reduce tasks and then broadcast the scheduling result to start pre-fetching on each worker.
% After that, when a map task is finished, each node will receive a broadcast message. 
SCache worker will filter the reduce tasks' IDs that are scheduled on itself and start pre-fetching shuffle data from the remote. 
% {\color{red}
% To enforce SCache pre-scheduled tasks -- node mapping, we insert some lines of codes in Spark DAG Scheduler.
% For RDDs with shuffle dependencies, Spark DAG scheduler will consult SCache master to get the preferred location for each partition and set \textit{NODE\_LOCAL} locality level on corresponding reduce tasks.
% }
{\color{blue}
In order to force DAG framework to run according to the SCache pre-scheduled results, we insert some lines of codes in framework scheduler.
After modification, DAG scheduler will consult SCache co-scheduler to get the preferred location for each task.
}
% In the case of extreme skew scenario, such as Figure \ref{fig:range_pre_sample}, Heuristic MinHeap trades about 0.05\% percent of stage completion time for 99\% reduction of shuffle data transmission through network by heuristicly swapping tasks.
% \begin{minipage}{\columnwidth}
% \begin{algorithm}[H]
% \caption{Accumulate Heuristic Scheduling for Multi-Shuffles}
% \label{mhminheap}
% 	\begin{algorithmic}[1]
% 	\small
% 	\Procedure{\Large m\_schedule}{$m, host\_id, p\_reduces, shuffles$}
% 		\State $m\gets$ partition number of map tasks
% 		\Comment $shuffles$ is the previous schedule result 
% 		\ForAll{$r$ in $p\_reduces$}
% 			\State $r.size \mathrel{+}= shuffles\left[r.rid\right].size$
% 			\If{$shuffles\left[r.rid\right].size\geq r.size \times r.prob$}
% 				\State $r.prob\gets shuffles\left[r.rid\right].size / r.size$
% 				\State $r.host\_id\gets shuffles\left[r.rid\right].assigned\_host$
% 			\EndIf
% 		\EndFor
% 		\State $M\gets$ $SCHEDULE\left(m, host\_id, p\_reduces\right)$
% 		\ForAll{$host\_id$ in $M$}
% 			\Comment Re-shuffle
% 			\ForAll{$r$ in $M\left[host\_id\right].reduces$}
% 				\If{$host\neq shuffles\left[r.rid\right].assigned\_host$}
% 				\State Re-shuffle data to $host$
% 				\State $shuffles\left[r.rid\right].assigned\_host\gets host$
% 				\EndIf
% 			\EndFor
% 		\EndFor
% 		\Return $M$
% 	\EndProcedure
% 	\end{algorithmic}
% \end{algorithm}
% \end{minipage}

@@

% {\color{red}
% \subsection{Cost of adapting DAG frameworks}
% SCache provides API through RPC, such as \textit{putBlock(blockId)}, \textit{getBlock(blockId)}, and \textit{getScheduleResult(shuffleId)}. The concise design makes it easy to adapt DAG frameworks to enable SCache optimization. For example, it only takes about 500 lines of code in Spark to integrate SCache. By a glance of Hadoop source code, we believe that the costs of enabling SCache on MapReduce \cite{hadoop} and YARN \cite{yarn} based DAG computing framework, such as Tez \cite{tez}, are also very low.
% }
{\color{blue}
\subsection{Analysis of cross-framework capability}\label{crossframework}
Shuffle optimization of SCache inevitably requires modification on dependent DAG framework. SCache provides API through RPC, such as \textit{putBlock (blockId)}, \textit{getBlock (blockId)}, and \textit{getScheduleResult (shuffleId)}. In order to use SCache, we mainly need to modify the two parts of the framework: (a)We need to insert codes in the DAG scheduler to let framework provide DAG information and follow the pre-scheduled result of SCache. (b)The shuffle data between the Map task and the Reduce task should be transferred to SCahce Storge Management.

To prove the cross-framework capability of SCache, we adapt SCache on Hadoop MapReduce and Spark respectively. Taking Hadoop MapReduce as an example, we insert codes in ResourceManager and modify codes in MapTask and ReduceTask to call SCache API through RPC. It takes about 400 lines of code. In Spark, we mainly modified the DAGScheduler and the corresponding data fetcher. 
It only takes about 500 lines of code. Such hundreds of lines of code modification are very small compared to the hundreds of thousands of lines of code in DAG framework. we believe that the costs of enabling SCache on other DAG computing frameworks, such as Tez \cite{tez}, are also very low.
}

>>>>

\section{Implementation}\label{impl}
This section presents an overview of the implementation of SCache. 
% {\color{red}
% Here we use Spark as an example of DAG framework to illustrate the work flow of shuffle optimization. 
% We will first present the system overview in Subsection \ref{arch} while the following two subsections focus on the two constraints on memory management.
% }
{\color{blue}
We first present the system overview and the detail of sampling in Subsection \ref{arch}. 
The following \ref{memorymanage} subsection focuses on two constraints on memory management.
In Subsection \ref{crossframework}, we evaluate cross-framework capability of SCache based on Hadoop MapReduce and Spark. 
At last, we discuss the cost of adapting SCache and fault tolerance. 
}

\subsection{System Overview}\label{arch}
SCache consists of three components: a distributed shuffle data management system, a DAG co-scheduler, and a %{\color{red}daemon inside Spark.}
{\color{blue} worker daemon. As a plug-in system, SCache needs to rely on a DAG framework.} As shown in Figure \ref{fig:architecture}, SCache employs the legacy master-slaves architecture like GFS \cite{gfs} for the shuffle data management system. 
The master node of SCache coordinates the shuffle blocks globally with application context. The worker node reserves memory to store blocks.
The coordination provides two guarantees: (a) data is stored in memory before tasks start and (b) data is scheduled on-off memory with all-or-nothing and context-aware constraints. 
The daemon bridges the communication between %{\color{red}Spark}
{\color{blue} DAG framework} and SCache. The co-scheduler is dedicated to pre-schedule reduce tasks with DAG information and enforce the scheduling results to %{\color{red}Spark scheduler}
 {\color{blue} original scheduler in framework}.

@@

When a map task finishes computing, the shuffle write implementation of DAG framework is modified to call the SCache API and move all the blocks out of {\color{blue}framework worker} through memory copy. 
After that, the slot will be released (without being blocked on disk operations).
When a block of the map output (i.e., "map output" in Figure \ref{fig:shuffle}) is received, the SCache worker will send the block ID and the size to the master.
If the collected map output data reach the observation threshold, the DAG co-scheduler will run the scheduling Algorithm \ref{hminheap} or \ref{mhminheap} to pre-schedule the reduce tasks and then broadcast the scheduling result to start pre-fetching on each worker.
% After that, when a map task is finished, each node will receive a broadcast message. 
SCache worker will filter the reduce tasks' IDs that are scheduled on itself and start pre-fetching shuffle data from the remote. 
% {\color{red}
% To enforce SCache pre-scheduled tasks -- node mapping, we insert some lines of codes in Spark DAG Scheduler.
% For RDDs with shuffle dependencies, Spark DAG scheduler will consult SCache master to get the preferred location for each partition and set \textit{NODE\_LOCAL} locality level on corresponding reduce tasks.
% }
{\color{blue}
In order to force DAG framework to run according to the SCache pre-scheduled results, we insert some lines of codes in framework scheduler.
After modification, DAG scheduler consults SCache co-scheduler to get the preferred location for each task.
}
% In the case of extreme skew scenario, such as Figure \ref{fig:range_pre_sample}, Heuristic MinHeap trades about 0.05\% percent of stage completion time for 99\% reduction of shuffle data transmission through network by heuristicly swapping tasks.
% \begin{minipage}{\columnwidth}
% \begin{algorithm}[H]
% \caption{Accumulate Heuristic Scheduling for Multi-Shuffles}
% \label{mhminheap}
% 	\begin{algorithmic}[1]
% 	\small
% 	\Procedure{\Large m\_schedule}{$m, host\_id, p\_reduces, shuffles$}
% 		\State $m\gets$ partition number of map tasks
% 		\Comment $shuffles$ is the previous schedule result 
% 		\ForAll{$r$ in $p\_reduces$}
% 			\State $r.size \mathrel{+}= shuffles\left[r.rid\right].size$
% 			\If{$shuffles\left[r.rid\right].size\geq r.size \times r.prob$}
% 				\State $r.prob\gets shuffles\left[r.rid\right].size / r.size$
% 				\State $r.host\_id\gets shuffles\left[r.rid\right].assigned\_host$
% 			\EndIf
% 		\EndFor
% 		\State $M\gets$ $SCHEDULE\left(m, host\_id, p\_reduces\right)$
% 		\ForAll{$host\_id$ in $M$}
% 			\Comment Re-shuffle
% 			\ForAll{$r$ in $M\left[host\_id\right].reduces$}
% 				\If{$host\neq shuffles\left[r.rid\right].assigned\_host$}
% 				\State Re-shuffle data to $host$
% 				\State $shuffles\left[r.rid\right].assigned\_host\gets host$
% 				\EndIf
% 			\EndFor
% 		\EndFor
% 		\Return $M$
% 	\EndProcedure
% 	\end{algorithmic}
% \end{algorithm}
% \end{minipage}

@@

% {\color{red}
% \subsection{Cost of adapting DAG frameworks}
% SCache provides API through RPC, such as \textit{putBlock(blockId)}, \textit{getBlock(blockId)}, and \textit{getScheduleResult(shuffleId)}. The concise design makes it easy to adapt DAG frameworks to enable SCache optimization. For example, it only takes about 500 lines of code in Spark to integrate SCache. By a glance of Hadoop source code, we believe that the costs of enabling SCache on MapReduce \cite{hadoop} and YARN \cite{yarn} based DAG computing framework, such as Tez \cite{tez}, are also very low.
% }
{\color{blue}
\subsection{Analysis of cross-framework capability}\label{crossframework}
Shuffle optimization of SCache inevitably requires modification on DAG frameworks. SCache provides APIs through RPC, such as \textit{putBlock (blockId)}, \textit{getBlock (blockId)}, and \textit{getScheduleResult (shuffleId)}. In order to use SCache, we mainly need to modify two parts of the frameworks: (a) We need to insert codes in the DAG scheduler to let framework provide DAG information and follow the pre-scheduled result of SCache. (b) The shuffle data between the map task and the reduce task should be transferred to SCahce Storge Management.

To prove the cross-framework capability of SCache, we adapt SCache on Hadoop MapReduce and Spark respectively. Taking Hadoop MapReduce as an example, we insert codes in ResourceManager and modify codes in MapTask and ReduceTask to call SCache API through RPC. It takes about 400 lines of code. In Spark, we mainly modified DAGScheduler and the corresponding data fetcher. 
It only takes about 500 lines of code. Such hundreds of lines of code modification are very small compared to the hundreds of thousands of lines of code in DAG framework. We believe that the costs of enabling SCache on other DAG computing frameworks, such as Tez \cite{tez}, are also very low.
}

### 2018-10-17 tex/intro.tex
SongTao revision.

\IEEEraisesectionheading{\section{Introduction}\label{sec:introduction}}
\IEEEPARstart{R}{ecent} years have witnessed the widespread use of sophisticated frameworks, such as Hadoop MapReduce\footnote{http://hadoop.apache.com/}, Dryad \cite{dryad}, Spark \cite{spark}, and Apache Tez \cite{tez}.
Most of them define jobs as directed acyclic graphs (DAGs), such as map-reduce pipeline in Hadoop MapReduce, lineage of resilient distributed datasets (RDDs) in Spark, vertices and edges in Dryad and Tez, etc.
Despite the differences among data-intensive frameworks, their communication is always structured as a shuffle phase,  which takes place between successive computation stages. 
Such shuffle phase places a significant burden for both the disk and network I/O, thus heavily affecting the end-to-end application performance. 
For instance, a MapReduce trace analysis from Facebook shows that shuffle accounts for 33\% of the job completion time on average, and up to 70\% in shuffle-heavy jobs \cite{managing}.

@@

{\color{blue}
In order to visually analyze above-mentioned resources scheduling, we propose a performance model called \textit{Framework Resources Quantification} (FRQ) model. FRQ model quantifies computing and I/O resources and displays resources scheduling strategy of DAG framework in the time dimension. We use FRQ model to assist in analyze the deficiencies of resources scheduling and optimize it. 
FRQ model has five parameters: \textit{Input Data Size, Data Conversion Rate, Computation Round Number, Computation Speed,} and \textit{Shuffle  Speed}.
According to the above five parameters and the scheduling strategy of the DAG framework, FRQ model is able to calculate the execution time of each phase of a computing job. 
Take Apache Hadoop MapReduce as a simple DAG computing example, we use FRQ to model each phase of the computing, including Map, Shuffle, and Reduce.
By revealing the relationships between the various phases, FRQ model assists us in discovering the irrationality of resource scheduling during computing.
I/O resource in map phase is not fully utilized. Furthermore, due to coupling with reduce phase, shuffle phase delays the execution time of reduce phase. 
This situation will be amplified in shuffle-heavy tasks.
}

@@

{\color{blue}
We have implemented SCache, a customized Apache Spark \cite{apachespark} and a customized Apache Hadoop. We have also designed a performance model called \textit{Framework Resources Quantification} (FRQ) model to analyze the shuffle optimization of SCache and calculate the execution time of each phase of a computing job. The performance of SCache is evaluated with both simulations and testbed experiments on a 50-node Amazon EC2 cluster on both Apache Spark and Apache Hadoop. On Apache Spark, we conduct basic test \textit{GroupByTest}. We also evaluate Terasort\footnote{https://github.com/ehiggs/spark-terasort} benchmark and standard workloads like TPC-DS\footnote{http://www.tpc.org/tpcds/} for multi-tenant modeling. On Apache Hadoop, we focus on Terasort benchmark. In a nutshell, SCache can eliminate explicit shuffle process by at most $89\%$ in varied applications. More impressively, SCache reduces $~40\%$ of overall completion time of TPC-DS queries on average on Apache Spark. On Apache Hadoop, SCache optimizes end-to-end Terasort completion time by 15\%.
}

>>>>

\IEEEraisesectionheading{\section{Introduction}\label{sec:introduction}}
\IEEEPARstart{R}{ecent} years have witnessed the widespread use of sophisticated frameworks, such as Hadoop MapReduce\footnote{http://hadoop.apache.com/}, Dryad \cite{dryad}, Spark \cite{spark}, and Apache Tez \cite{tez}.
Most of them define jobs as directed acyclic graphs (DAGs), such as map-reduce pipeline in Hadoop MapReduce, lineage of resilient distributed datasets (RDDs) in Spark, vertices and edges in Dryad and Tez, etc.
Despite the differences among data-intensive frameworks, their communication is always structured as a shuffle phase,  which takes place between successive computation stages. 
Such shuffle phase places a significant burden for both the disk and network I/O, thus heavily affecting the end-to-end application performance. 
For instance, a MapReduce trace analysis from Facebook shows that shuffle accounts for $33\%$ of the job completion time on average, and up to $70\%$ in shuffle-heavy jobs \cite{managing}.

@@

{\color{blue}
In order to visually analyze above-mentioned resources scheduling, we propose a performance model called \textit{Framework Resources Quantification} (FRQ) model. The FRQ model quantifies computing and I/O resources and displays resources scheduling strategy of DAG framework in the time dimension. We use the FRQ model to assist in analyze the deficiencies of resources scheduling and optimize it. 
The FRQ model has five parameters: \textit{Input Data Size, Data Conversion Rate, Computation Round Number, Computation Speed,} and \textit{Shuffle  Speed}.
According to the above five parameters and the scheduling strategy of the DAG framework, the FRQ model is able to calculate the execution time of each phase of a computing job. 
Taking Apache Hadoop MapReduce as a simple DAG computing example, we model each phase of the computing by the FRQ model, including Map, Shuffle and Reduce.
By revealing the relationships between the various phases, the FRQ model assists us in discovering the irrationality of resource scheduling during computing.
I/O resource in the map phase is not fully utilized. Furthermore, due to coupling with reduce phase, shuffle phase delays the execution time of reduce phase. 
This situation will be amplified in shuffle-heavy tasks.
}

@@

{\color{blue}
We have implemented SCache on both Apache Spark \cite{apachespark} and Hadoop MapReduce. We have also designed a performance model called \textit{Framework Resources Quantification} (FRQ) model to analyze the shuffle optimization of SCache and calculate the execution time of each phase of a computing job. The performance of SCache is evaluated with both simulations and testbed experiments on a 50-node Amazon EC2 cluster on both Apache Spark and Apache Hadoop. On Apache Spark, we conduct a basic test - \textit{GroupByTest}. We also evaluate the system with Terasort\footnote{https://github.com/ehiggs/spark-terasort} benchmark and standard workloads like TPC-DS\footnote{http://www.tpc.org/tpcds/} for multi-tenant modeling. On Apache Hadoop, we focus on Terasort benchmark. In a nutshell, SCache can eliminate explicit shuffle time by at most $89\%$ in varied applications. More impressively, SCache reduces $~40\%$ of overall completion time of TPC-DS queries on average on Apache Spark. On Apache Hadoop, SCache optimizes end-to-end Terasort completion time by $15\%$.
}
